---
title: "Supplementary Material (Wu et al.) -- Analysis Script"
author: "Zezhen Wu"
date: "2023-12-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load cleaned data files
```{r}
# Because Bayesian models are time-consuming, we stored all the modeling outputs in an RData file, and provide the original codes that generated these models below

# You can download the RData file from OSF and load it here with a correctly-specified file path
#load("/Users/michaelfive/Library/CloudStorage/GoogleDrive-wuzezhen33@gmail.com/My Drive/Nepal SA Study/Analysis/model/gr6-10_survey_gpa_1019.RData")

# load("~/gr6-10_survey_gpa_1019.RData")
```

# Data preparation

```{r data preparation, include = F}
# Workflow management
library(targets)
# Data wrangling
library(tidyverse)
# Missing data check
library(mice)
library(naniar)
# Bayesian modeling
library(brms)
library(bayestestR)
# Reporting
library(performance)
library(broom.mixed)
library(bayesplot)
library(interactions)

# Utility functions
source("R/functions.R")

# Stan option
options(mc.cores = parallel::detectCores())

# `dat_s` is the main de-identified dataset
```

# Missingness Check

```{r}
# Tests the null hypothesis that the missing data is Missing Completely At Random (MCAR). A p.value of less than 0.05 is usually interpreted as being that the missing data is not MCAR (i.e., is either Missing At Random or non-ignorable).

test <- dat_s |> select(
      st_id, all_gpa_e, all_gpa_b, fscore_f1_b, fscore_f1_e, fscore_f2_b, fscore_f2_e, fscore_f3_b, fscore_f3_e, treated_int, class_size, grade, gender, age_b, 
      father_edu_f, mother_edu_f, 
      father_occ_salary, mother_occ_salary, adult_members, siblings, duration_int)

#   statistic    df p.value missing.patterns
#       <dbl> <dbl>   <dbl>            <int>
# 1      183.   173   0.288               12
naniar::mcar_test(test)

mice::md.pattern(test, rotate.names = T)
# We believe the missing data is MCAR, because we know the missingness has random and distinct reasons.

# 32 missing all endline survey data because they were not in school during the data collection for non-academic reasons
# 10 missing GPA either because they did not take the exam or school record entry errors
# 1 missing both survey and GPA
# 1 missing baseline age potentially due to entry error
# 1 + 6 missing all baseline data because no presence during data collection
# 1 + 1 missing all baseline and endline data because no presence during data collection
# 3 missing intervention data because of no presence during data collection
# 3 missing intervention and endline because of no presence during data collection

# So it seems reasonable to conduct complete-cases analysis.
```

# Descriptive statistics
```{r}
# The following statistics/plots are calculated as evidence in the impact evaluation manuscript.

# number of students
length(unique(dat_s$st_id))

# school summary stats
table(dat_s$sch_id)
table(dat_s$sch_id, dat_s$grade, dat_s$treated_int)

# gender summary stats
prop.table(table(dat_s$gender))

# grade summary stats
prop.table(table(dat_s$grade))

# age summary stats
mean(dat_s$age_b, na.rm = T)
sd(dat_s$age_b, na.rm = T)

# treatment alloocation
table(dat_s$treated_int)

# number of hearing students
table(dat_s$student_type)

# GPA by school and treatment condition
df <- dat_s |> select(
      st_id, sch_id, fscore_f1_e, fscore_f1_b, fscore_f2_e, fscore_f2_b, fscore_f3_e, fscore_f3_b, treated_int, class_size, grade, gender, age_b, 
      father_edu_f, mother_edu_f, 
      father_occ_salary, mother_occ_salary, adult_members, siblings, duration_int) |> 
  na.omit() |> 
  group_by(sch_id, treated_int) |> 
  summarise(
    m_f1_e = mean(fscore_f1_e, na.rm = T),
    sd_f1_e = sd(fscore_f1_e, na.rm = T),
    m_f1_b = mean(fscore_f1_b, na.rm = T),
    sd_f1_b = sd(fscore_f1_b, na.rm = T),
    m_f2_e = mean(fscore_f2_e, na.rm = T),
    sd_f2_e = sd(fscore_f2_e, na.rm = T),
    m_f2_b = mean(fscore_f2_b, na.rm = T),
    sd_f2_b = sd(fscore_f2_b, na.rm = T),
    m_f3_e = mean(fscore_f3_e, na.rm = T),
    sd_f3_e = sd(fscore_f3_e, na.rm = T),
    m_f3_b = mean(fscore_f3_b, na.rm = T),
    sd_f3_b = sd(fscore_f3_b, na.rm = T),
    n = n()
  ); df

# GPA by school
dat_s |> group_by(sch_id) |> reframe(m = mean(all_gpa_e, na.rm = T))
dat_s |> group_by(sch_id) |> reframe(m = mean(all_gpa_b, na.rm = T))

# GPA summary stats
mean(dat_s$all_gpa_b, na.rm = T)
mean(dat_s$all_gpa_e, na.rm = T)
sd(dat_s$all_gpa_b, na.rm = T)
sd(dat_s$all_gpa_e, na.rm = T)

# Psychological well-being summary stats
mean(dat_s$fscore_f1_b, na.rm = T)
mean(dat_s$fscore_f2_b, na.rm = T)
mean(dat_s$fscore_f3_b, na.rm = T)
mean(dat_s$fscore_f1_e, na.rm = T)
mean(dat_s$fscore_f2_e, na.rm = T)
mean(dat_s$fscore_f3_e, na.rm = T)

# Manipulation check
dat_s |> group_by(treated_int) |> summarise(m = mean(mc_survey_1_int, na.rm = T))
dat_s |> group_by(treated_int) |> summarise(m = mean(mc_survey_2_int, na.rm = T))
dat_s |> group_by(treated_int) |> summarise(m = mean(mc_survey_3_int, na.rm = T))
dat_s |> group_by(treated_int) |> summarise(m = mean(mc_survey_4_int, na.rm = T))
```

```{r}
# Figure 2
df <- dat_s |> 
  group_by(treated_int, class_id) |>
  mutate(class_id = as.numeric(class_id)) |> 
  summarise(m_b = mean(all_gpa_b, na.rm = T),
            se_b = sd(all_gpa_b, na.rm = T)/sqrt(length(all_gpa_b)),
            m_e = mean(all_gpa_e, na.rm = T),
            se_e = sd(all_gpa_e, na.rm = T)/sqrt(length(all_gpa_e))
            )

df <- df |> 
  pivot_longer(cols = m_b:se_e,
               names_to = c("stat", "time"),
               names_pattern = "(.*)_(.*)",
               values_to = "value")

df <- df |> 
  pivot_wider(names_from = "stat", values_from = "value")

df <- df |> 
  mutate(treated_int = ifelse(treated_int == 1,
                              "Treatment",
                              "Control")
         )  |> 
  mutate(class_id = case_when(
           class_id %in% c(1:5) ~ paste0("School A Grade ", class_id + 5),
           class_id %in% c(8:12) ~ paste0("School B Grade ", class_id - 2),
           class_id %in% c(15:19) ~ paste0("School C Grade ", class_id - 9)
         )) |> 
  mutate(class_id = factor(class_id,
                           levels = c(
                             paste0("School A Grade ", 6:10),
                             paste0("School B Grade ", 6:10),
                             paste0("School C Grade ", 6:10)
                           ))) |> 
  rename(Condition = treated_int)

df <- df |> 
  mutate(time = ifelse(time == "b", "Baseline", "Endline"))

ggplot(data = df,
       aes(x = time, y = m, group = Condition,
           color = Condition)) +
  geom_line(position=position_dodge(0.2))+
  geom_point(size = 2, position=position_dodge(0.2)) +
  geom_errorbar(aes(ymin=m-se, ymax=m+se), width=.2,
                 position=position_dodge(0.2)) +
  labs(x = "", y = "GPA\n",
       title = "Average GPA at Baseline and Endline\nby Treatment Conditions and Classes\n",
       caption = "(Each error bar shows the standard error of the group mean.)") +
  facet_wrap(~class_id, nrow = 3) +
  theme_minimal() +
  theme(plot.caption.position = "plot",
        plot.caption = element_text(hjust = 0.5),
        plot.title = element_text(hjust = 0.5, face = "bold")) +
   scale_color_manual(values=c('firebrick1','steelblue1')) + 
  ylim(c(1,3.5))

```

```{r}
# correlation matrix
cor_df <- corstarsl(dat_s |> ungroup() |> select(fscore_f1_b:fscore_f3_b, all_gpa_b,
                                                 fscore_f1_e:fscore_f3_e, all_gpa_e))

rownames(cor_df) <- c("1. Self-integrity and Belonging in School (Baseline)",
                      "2. Stereotype Threat (Baseline)",
                      "3. Academic Stress (Baseline)",
                      "4. Grade Point Average (Baseline)",
                      "5. Self-integrity and Belonging in School (Endline)",
                      "6. Stereotype Threat (Endline)",
                      "7. Academic Stress (Endline)",
                      "8. Grade Point Average (Endline)")

colnames(cor_df) <- as.character(c(1:8))

write.csv(cor_df, "analysis/tables/tab_cor.csv")
```

# Differential Attrition

```{r}
temp <- dat_s |> mutate(has_gpa_e = !is.na(all_gpa_e))

mod_attr <- stan_glm(has_gpa_e ~ treated_int * (age_b + gender), data = temp, family = "binomial", seed = 1234)

summary(mod_attr, digits = 3)
```

# Analysis

## Prior predictive checks

```{r check priors}
# priors to be tested
my_prior <- prior("normal(0, 1)", class = "b")

# check default priors for other parameters
validate_prior(
    my_prior,
    fscore_f1_e ~ fscore_f1_b + treated_int +
    class_size + grade + gender + age_b + student_type + father_edu_f + mother_edu_f +
    father_occ_salary + mother_occ_salary + adult_members + siblings + duration_int +
    (treated_int | class_id),
  dat_s)
```

## Primary outcomes

```{r}
fit_gpa <- brm(
    all_gpa_e ~ all_gpa_b + treated_int +
      class_size + grade + gender + age_b + student_type + father_edu_f + mother_edu_f +
      father_occ_salary + mother_occ_salary + adult_members + siblings + duration_int + sch_id +
      (treated_int | class_id),
    dat_s,
    prior = my_prior, 
    chains = 4,
    seed = 1234,
    control = list(adapt_delta = 0.99,
                   max_treedepth = 15)
  )
```

```{r}
# posterior predictive checks suggest pretty good fit
p1 <- pp_check(fit_gpa, ndraws = 200) +
  labs(title = "Posterior predictive checking for the model\npredicting GPA", 
       x = "GPA", 
       y = "Density") + 
  xlim(-5,5) +
  theme_classic();p1

# loo suggests good predictive performance (not necessary though if I wish to focusing on interpreting the model parameters)
loo_gpa <- loo(fit_gpa, reloo = T)
```

```{r}
# hypothesis test
hypothesis(fit_gpa, "treated_int > 0")

# Figure 1
draws <- as_draws_df(fit_gpa)

plot.kdensity(draws$b_treated_int, value = 0,
              xlab = "Estimated Difference (Treatment - Control)",
              main = "Posterior Distribution of the Treatment Effect of\n Values Affirmation on Nepalese Deaf Students' GPA",
              col1 = "steelblue1",
              col2 = "firebrick1")

# Add ROPE: a shaded rectangle between the lines
rect(-sd(dat_s$all_gpa_e, na.rm = T) * 0.02,
     0, 
     sd(dat_s$all_gpa_e, na.rm = T) * 0.02,
     16, col = rgb(1, 0.5, 0, alpha = 0.5), border = NA)

# 95% high-density interval for reporting
hdi(fit_gpa, ci = 0.89)

# posterior draws of Cohen's d effect size
summary(get.posterior.treat.d(fit_gpa))

# Sequential Effect eXistence and sIgnificance Testing (SEXIT) framework
# using the empirical benchmark in Kraft (2020)
sexit(fit_gpa, significant = 0.02 * sd(dat_s$all_gpa_e, na.rm = T), large = 0.05 * sd(dat_s$all_gpa_e, na.rm = T), ci = 0.89)[3,]

# consider es = 0.01 as negligible
rope(fit_gpa, ci = 0.89, 
     range = c(-sd(dat_s$all_gpa_e, na.rm = T) * 0.02, 
               sd(dat_s$all_gpa_e, na.rm = T) * 0.02))

# treatment heterogeneity of the main model across classrooms
summary(fit_gpa)$random

posterior_samples <- as_draws(fit_gpa, pars = "^class_id")
hdi(posterior_samples, ci = 0.89)

```

## Secondary outcomes

```{r}
# Self-efficacy and sense of belonging in school
fit_f1 <- brm(
    fscore_f1_e ~ fscore_f1_b + treated_int +
      class_size + grade + gender + age_b + student_type + father_edu_f + mother_edu_f +
      father_occ_salary + mother_occ_salary + adult_members + siblings + duration_int + sch_id + all_gpa_b + 
      (treated_int | class_id),
    dat_s,
    prior = my_prior, 
    chains = 4,
    seed = 1234,
    control = list(adapt_delta = 0.99,
                   max_treedepth = 15)
  )

# Stereotype threat  
fit_f2 <- brm(
    fscore_f2_e ~ fscore_f2_b + treated_int +
      class_size + grade + gender + age_b + student_type + father_edu_f + mother_edu_f +
      father_occ_salary + mother_occ_salary + adult_members + siblings + duration_int + sch_id + all_gpa_b +
      (treated_int | class_id),
    dat_s,
    prior = my_prior, 
    chains = 4,
    seed = 1234,
    control = list(adapt_delta = 0.99,
                   max_treedepth = 15)
  )
 
# Academic stress 
fit_f3 <- brm(
    fscore_f3_e ~ fscore_f3_b + treated_int +
      class_size + grade + gender + age_b + student_type + father_edu_f + mother_edu_f +
      father_occ_salary + mother_occ_salary + adult_members + siblings + duration_int + sch_id + all_gpa_b +
      (treated_int | class_id),
    dat_s,
    prior = my_prior, 
    chains = 4,
    seed = 1234,
    control = list(adapt_delta = 0.99,
                   max_treedepth = 15))
```

```{r}
summary(fit_f1$rhats)# pretty good rhats
summary(fit_f2$rhats) # pretty good rhats
summary(fit_f3$rhats) # pretty good rhats

# posterior predictive checks suggest pretty good fit
p1 <- pp_check(fit_f1, ndraws = 200) +
  labs(title = "Posterior predictive checking for the model\npredicting self-esteem", 
       x = "Self-esteem", 
       y = "Density") + 
  xlim(-5,5) +
  theme_classic();p1

p2 <- pp_check(fit_f2, ndraws = 200) +
  labs(title = "Posterior predictive checking for the model\npredicting stereotype threat", 
       x = "Stereotype Threat", 
       y = "Density") + 
  xlim(-5,5) +
  theme_classic();p2

p3 <- pp_check(fit_f3, ndraws = 200) +
  labs(title = "Posterior predictive checking for the model\npredicting academic stress", 
       x = "Academic Stress", 
       y = "Density") + 
  xlim(-5,5) +
  theme_classic();p3

# loo suggests good predictive performance
loo_f1 <- loo(fit_f1, reloo = T)
loo_f2 <- loo(fit_f2, reloo = T)
loo_f3 <- loo(fit_f3, reloo = T)
```

```{r}
# hypothesis tests
hypothesis(fit_f1, "treated_int > 0") #
hypothesis(fit_f2, "treated_int < 0") #
hypothesis(fit_f3, "treated_int < 0")

# Figure 3
par(mfrow = c(1, 3))

draws <- as_draws_df(fit_f2)

plot.kdensity(draws$b_treated_int, value = 0,
              xlab = "Estimated Difference (Treatment - Control)",
              main = "Posterior Distribution of the Treatment Effect\non Reducing Stereotype Threat")

# abline(v = c(-0.37, 0.06), col = "orange", lwd = 3)
# Add ROPE: a shaded rectangle between the lines
rect(-0.02, 0, 0.02, 4, col = rgb(1, 0.5, 0, alpha = 0.5), border = NA)

# posterior predictive plots
draws <- as_draws_df(fit_f1)

plot.kdensity(draws$b_treated_int, value = 0,
              xlab = "Estimated Difference (Treatment - Control)",
              main = "Posterior Distribution of the Treatment Effect on\nPromoting Self-efficacy and Sense of Belonging in School",
              col1 = "steelblue1",
              col2 = "firebrick1")

# Add ROPE: a shaded rectangle between the lines
rect(-0.02, 0, 0.02, 4, col = rgb(1, 0.5, 0, alpha = 0.5), border = NA)

draws <- as_draws_df(fit_f3)

plot.kdensity(draws$b_treated_int, value = 0,
              xlab = "Estimated Difference (Treatment - Control)",
              main = "Posterior Distribution of the Treatment Effect\non Reducing Academic Stress")

# Add ROPE: a shaded rectangle between the lines
rect(-0.02, 0, 0.02, 4, col = rgb(1, 0.5, 0, alpha = 0.5), border = NA)


# 95% high-density interval for reporting
hdi(fit_f1, ci = 0.89)
hdi(fit_f2, ci = 0.89)
hdi(fit_f3, ci = 0.89)

# posterior draws of Cohen's d effect size
hist(get.posterior.treat.d(fit_f1))
hist(get.posterior.treat.d(fit_f2))
hist(get.posterior.treat.d(fit_f3))

# sexit reporting based on empirical benchmarks in Bakker et al., 2019 and Kraft, 2020: small = 0.05, medium = 0.15, large = 0.2

# Sequential Effect eXistence and sIgnificance Testing (SEXIT) framework
sexit(fit_f1, significant = 0.02 * sd(dat_s$fscore_f1_e, na.rm = T), ci = 0.89)[3,]
sexit(fit_f2, significant = 0.02 * sd(dat_s$fscore_f2_e, na.rm = T), ci = 0.89)[3,]
sexit(fit_f3, significant = 0.02 * sd(dat_s$fscore_f3_e, na.rm = T), ci = 0.89)[3,]

rope(fit_f1, range = c(-0.02 * sd(dat_s$fscore_f2_e, na.rm = T), 0.02 * sd(dat_s$fscore_f2_e, na.rm = T)), ci = 0.89)
rope(fit_f2, range = c(-0.02 * sd(dat_s$fscore_f2_e, na.rm = T), 0.02 * sd(dat_s$fscore_f2_e, na.rm = T)), ci = 0.89)
rope(fit_f3, range = c(-0.02 * sd(dat_s$fscore_f2_e, na.rm = T), 0.02 * sd(dat_s$fscore_f2_e, na.rm = T)), ci = 0.89)
```

## Moderation effect (school subgroup)

```{r}
fit_gpa_x_sch_id <- brm(
    all_gpa_e ~ all_gpa_b + treated_int * sch_id +
      class_size + grade + gender + age_b + student_type + father_edu_f + mother_edu_f +
      father_occ_salary + mother_occ_salary + adult_members + siblings + duration_int +
      (treated_int | class_id),
    dat_s,
    prior = my_prior, 
    chains = 4,
    seed = 1234,
    control = list(adapt_delta = 0.99,
                   max_treedepth = 15)
  )

interact_plot(model = fit_gpa_x_sch_id, 
              pred = "treated_int", 
              modx = "sch_id",
              legend.main = "School",
              pred.labels = c("Control", "Treatment"),
              x.label = "\nTreatment Condition",
              y.label = "Core Course GPA\n")
```


## Moderation effect (prior performance)

```{r}
# create low-performing variable (according to pre-registration)
dat_s <- dat_s |> 
  group_by(class_id) |> 
  mutate(low_performing = as.numeric(all_gpa_b <= median(all_gpa_b)))
```

```{r}
# using baseline performance (dichotomous) as the moderator
fit_gpa_x_low_performance <- brm(
    all_gpa_e ~ all_gpa_b + treated_int * low_performing +
      class_size + grade + gender + age_b + student_type +
      father_edu_f + mother_edu_f +
      father_occ_salary + mother_occ_salary + adult_members + siblings + duration_int + sch_id +
      (treated_int | class_id),
    data = dat_s,
    prior = my_prior, 
    chains = 4,
    seed = 1234,
    control = list(adapt_delta = 0.99,
                   max_treedepth = 15)
  )

hypothesis(fit_gpa_x_low_performance, "treated_int > 0")

hypothesis(fit_gpa_x_low_performance, "treated_int:low_performing < 0")

hdi(fit_gpa_x_low_performance, ci = 0.89)
sexit(fit_gpa_x_low_performance)
```

```{r}
# using baseline performance (continuous) as the moderator
fit_gpa_x_low_performance_cont <- brm(
    all_gpa_e ~ all_gpa_b + treated_int * all_gpa_b +
      class_size + grade + gender + age_b + student_type +
      father_edu_f + mother_edu_f +
      father_occ_salary + mother_occ_salary + adult_members + siblings + duration_int + sch_id +
      (treated_int | class_id),
    data = dat_s,
    prior = my_prior, 
    chains = 4,
    seed = 1234,
    control = list(adapt_delta = 0.99,
                   max_treedepth = 15)
  )

hypothesis(fit_gpa_x_low_performance_cont, "treated_int > 0")

hypothesis(fit_gpa_x_low_performance_cont, "all_gpa_b:treated_int < 0")

hdi(fit_gpa_x_low_performance_cont, ci = 0.89)
sexit(fit_gpa_x_low_performance_cont)
```

## Moderation effect (psychological threat)

### Composite psychological threat (average of all three factors)

```{r}
dat_s$fscore_f1_b_rev <- -dat_s$fscore_f1_b

dat_s$psych_threat <- rowMeans(dat_s[, c("fscore_f1_b_rev", "fscore_f2_b", "fscore_f2_b")], na.rm = T)

hist(dat_s$psych_threat)

fit_gpa_x_psych_threat <- brm(
    all_gpa_e ~ all_gpa_b + treated_int * psych_threat + class_size + grade + gender + age_b + student_type +
      father_edu_f + mother_edu_f +
      father_occ_salary + mother_occ_salary + adult_members + siblings + duration_int + sch_id +
      (treated_int | class_id),
    data = dat_s,
    prior = my_prior, 
    chains = 4,
    seed = 1234,
    control = list(adapt_delta = 0.99,
                   max_treedepth = 15))
```

```{r}
hypothesis(fit_gpa_x_psych_threat, "treated_int > 0")
hypothesis(fit_gpa_x_psych_threat, "treated_int:psych_threat < 0")

hdi(fit_gpa_x_psych_threat, ci = 0.89)

# consider es = 0.02 as negligible
rope(fit_gpa_x_psych_threat, ci = 0.89, 
     range = c(-sd(dat_s$all_gpa_e, na.rm = T) * 0.02, 
               sd(dat_s$all_gpa_e, na.rm = T) * 0.02))

# using the empirical benchmark in Kraft (2020)
sexit(fit_gpa_x_psych_threat, significant = 0.05 * sd(dat_s$all_gpa_e, na.rm = T), large = 0.2 * sd(dat_s$all_gpa_e, na.rm = T), ci = 0.89)[3,]


p1 <- interact_plot(model = fit_gpa_x_psych_threat, 
              pred = "treated_int", 
              modx = "psych_threat",
              legend.main = "Psychological Threat",
              pred.labels = c("Control", "Treatment"),
              x.label = "\nTreatment Condition",
              y.label = "GPA\n") + 
  theme_minimal();p1
```

```{r}
# simple slope effect
dat_s <- dat_s |> 
  mutate(psych_threat_p1sd = psych_threat + sd(psych_threat, na.rm = T),
         psych_threat_m1sd = psych_threat - sd(psych_threat, na.rm = T))

# treatment effect for high threat
fit_gpa_x_psych_threat_high <- brm(
    all_gpa_e ~ all_gpa_b + treated_int * psych_threat_m1sd + class_size + grade + gender + age_b + student_type +
      father_edu_f + mother_edu_f +
      father_occ_salary + mother_occ_salary + adult_members + siblings + duration_int + sch_id +
      (treated_int | class_id),
    data = dat_s,
    prior = my_prior, 
    chains = 4,
    seed = 1234,
    control = list(adapt_delta = 0.99,
                   max_treedepth = 15))

hypothesis(fit_gpa_x_psych_threat_high, "treated_int > 0")
hdi(fit_gpa_x_psych_threat_high, ci = 0.89)

# treatment effect for low threat
fit_gpa_x_psych_threat_low <- brm(
    all_gpa_e ~ all_gpa_b + treated_int * psych_threat_p1sd + class_size + grade + gender + age_b + student_type +
      father_edu_f + mother_edu_f +
      father_occ_salary + mother_occ_salary + adult_members + siblings + duration_int + sch_id +
      (treated_int | class_id),
    data = dat_s,
    prior = my_prior, 
    chains = 4,
    seed = 1234,
    control = list(adapt_delta = 0.99,
                   max_treedepth = 15))

hypothesis(fit_gpa_x_psych_threat_low, "treated_int > 0")
hdi(fit_gpa_x_psych_threat_low, ci = 0.89)
```

### Stereotype threat only

```{r}
hist(dat_s$fscore_f2_b)

fit_gpa_x_stereotype_threat <- brm(
    all_gpa_e ~ all_gpa_b + treated_int * fscore_f2_b + class_size + grade + gender + age_b + student_type + 
      father_edu_f + mother_edu_f +
      father_occ_salary + mother_occ_salary + adult_members + siblings + duration_int + sch_id +
      (treated_int | class_id),
    data = dat_s,
    prior = my_prior, 
    chains = 4,
    seed = 1234,
    control = list(adapt_delta = 0.99,
                   max_treedepth = 15))
```

```{r}
hypothesis(fit_gpa_x_stereotype_threat, "treated_int > 0")
hypothesis(fit_gpa_x_stereotype_threat, "treated_int:fscore_f2_b < 0")

hdi(fit_gpa_x_stereotype_threat, ci = 0.89)

# consider es = 0.01 as negligible
rope(fit_gpa_x_stereotype_threat, ci = 0.89, 
     range = c(-sd(dat_s$all_gpa_e, na.rm = T) * 0.01, 
               sd(dat_s$all_gpa_e, na.rm = T) * 0.01))

# using the empirical benchmark in Kraft (2020)
sexit(fit_gpa_x_stereotype_threat, significant = 0.05 * sd(dat_s$all_gpa_e, na.rm = T), large = 0.2 * sd(dat_s$all_gpa_e, na.rm = T), ci = 0.89)[3,]


p2 <- interact_plot(model = fit_gpa_x_stereotype_threat, 
              pred = "treated_int", 
              modx = "fscore_f2_b",
              legend.main = "Stereotype Threat",
              pred.labels = c("Control", "Treatment"),
              x.label = "\nTreatment Condition",
              y.label = "GPA\n") + theme_minimal(); p2

# Figure 4
gridExtra::grid.arrange(p1, p2, nrow = 1)
```

```{r}
# simple slope effect
dat_s <- dat_s |> 
  mutate(fscore_f2_b_p1sd = fscore_f2_b + sd(fscore_f2_b, na.rm = T),
         fscore_f2_b_m1sd = fscore_f2_b - sd(fscore_f2_b, na.rm = T))

# treatment effect for high threat
fit_gpa_x_stereotype_threat_high <- brm(
    all_gpa_e ~ all_gpa_b + treated_int * fscore_f2_b_m1sd + class_size + grade + gender + age_b + student_type +
      father_edu_f + mother_edu_f +
      father_occ_salary + mother_occ_salary + adult_members + siblings + duration_int + sch_id +
      (treated_int | class_id),
    data = dat_s,
    prior = my_prior, 
    chains = 4,
    seed = 1234,
    control = list(adapt_delta = 0.99,
                   max_treedepth = 15))

hypothesis(fit_gpa_x_stereotype_threat_high, "treated_int > 0")
hdi(fit_gpa_x_stereotype_threat_high, ci = 0.89)

# treatment effect for low threat
fit_gpa_x_stereotype_threat_low <- brm(
    all_gpa_e ~ all_gpa_b + treated_int * fscore_f2_b_p1sd + class_size + grade + gender + age_b + student_type +
      father_edu_f + mother_edu_f +
      father_occ_salary + mother_occ_salary + adult_members + siblings + duration_int + sch_id +
      (treated_int | class_id),
    data = dat_s,
    prior = my_prior, 
    chains = 4,
    seed = 1234,
    control = list(adapt_delta = 0.99,
                   max_treedepth = 15))

hypothesis(fit_gpa_x_stereotype_threat_low, "treated_int > 0")
hdi(fit_gpa_x_stereotype_threat_low, ci = 0.89)
```

## Mediation Model

```{r}
# Stereotype threat as a mediator (explorative analysis based on pre-registration)

# Mediator model
mediator_model <- bf(fscore_f2_e ~ fscore_f2_b + treated_int + class_size + grade + gender + age_b + student_type + father_edu_f + mother_edu_f + father_occ_salary + mother_occ_salary + adult_members + siblings + duration_int + (treated_int | class_id))

# Outcome model with mediator (fscore_f2_e) included
outcome_model <- bf(all_gpa_e ~ all_gpa_b + fscore_f2_e + treated_int + class_size + grade + gender + age_b + student_type + father_edu_f + mother_edu_f + father_occ_salary + mother_occ_salary + adult_members + siblings + duration_int + (treated_int | class_id))

# Fit the Bayesian mediation model
mediation_model <- brm(mediator_model + outcome_model + set_rescor(FALSE),
                       data = dat_s, 
                       prior = my_prior,
                       chains = 4,
                       seed = 1234)

# not mediated through stereotype threat
mediation(mediation_model, method = "HDI")
```